\documentclass[12pt, titlepage, a4paper]{article}
\usepackage{subfiles}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\graphicspath{ {images/} }
\usepackage{hyperref}

\title{Perceptrons: An Overview}
\author{Harjas Monga and Vidhur Kumar}

\begin{document}
	\maketitle
	
	\tableofcontents
	
	\newpage

	\textit{"We expect the perceptron to be the embryo of an electronic computer that will be able to walk, talk, see, write, reproduce itself and be conscious of its existence."} - The New York Times, 1958.	
	
	\section{What this report entails}
		\subfile{sections/p1}	
	\section{Introduction: What is a Perceptron?}
		\subfile{sections/p2}
	\section{Workings: What drives a Perceptron?}
		\subfile{sections/p3}
	\section{Applications: What can I do with a Perceptron?}
		\subfile{sections/p4}
	\section{Conclusion: The Authors' Personal Thoughts}
		\subfile{sections/p5}
		
		\newpage
		
	\begin{thebibliography}{1}

	\bibitem{book} Nielse, N. A. (2017, December 02). {\em Neural Networks and Deep Learning.} Retrieved March 25, 2018, from\\ {http://neuralnetworksanddeeplearning.com/chap1.html}

  	\bibitem{image1} Karim, R. (2016, December 12). {\em Deep Learning via Multilayer Perceptron Classifier - DZone Big Data}. Retrieved March 30, 2018, from \\ \url{https://dzone.com/articles/deep-learning-via-multilayer-perceptron-classifier}

  	\bibitem{image2} Smuc, T. (n.d.). {\em Neural Networks}. Retrieved March 27, 2018, from\\ \url{http://dms.irb.hr/tutorial/tut_nnets_short.php}
  	
  	\bibitem{image3} Franzen, C. (2016, January 18). {\em Multiple Regression in Python- Gradient Descent}. Retrieved April 01, 2018, from\\ \url{http://charlesfranzen.com/posts/multiple-regression-in-python-gradient-descent/}


  \end{thebibliography}

\end{document}